---
title: 'Tidy Tuesday #1'
author: "Jenny Li"
output: 
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(tidyverse)     # for graphing and data cleaning
library(lubridate)     # for date manipulation
library(ggthemes)      # for even more plotting themes
library(janitor)       # for cleaning variable names
library(geofacet)      # for special faceting with US map layout
library(dplyr)
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
Sys.setlocale("LC_TIME", "English")
theme_set(theme_minimal())       
```

### Chart type
map

### Type of data
NA

### Reason for including the chart
TidyTuesday

### Link to data or source
[github repository page](https://github.com/rfordatascience/tidytuesday/tree/master/data/2022/2022-08-09)

### Research Question
What is the distribution of wheels around the world?

## Read in data for this week: 
```{r}
# Get the Data

# Read in with tidytuesdayR package 
#Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

tuesdata <- tidytuesdayR::tt_load('2022-08-09')
tuesdata <- tidytuesdayR::tt_load(2022, week = 32)

wheels <- tuesdata$wheels

# Or read in the data manually

wheels <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-08-09/wheels.csv')
world <- map_data("world")
```
## Graph
```{r, fig.alt="map showing the number of wheels around the world"}
newWheels<- wheels %>% 
  group_by(country) %>% 
  summarise(number=n())

newWheels  %>%
  ggplot() +
  geom_map(map = world,
           aes(map_id = country,
               fill = number )) +
  scale_fill_continuous(type = "viridis") +
  labs(title = "Distribution of Wheels Around the World", fill = "Number of Wheels") +
  expand_limits(x = world$long, y = world$lat) +
  theme_map()+
  theme(legend.position = "right")
```
## Most of countries around the world contains less than five wheels or even no wheel. USA contains the most wheels around the world, over 15, following by Japan and China which is around 15 and 10.


