---
title: "TidyTuesday9-20"
author: "Jenny Li"
output: 
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(tidyverse)     # for graphing and data cleaning
library(lubridate)     # for date manipulation
library(ggthemes)      # for even more plotting themes
library(janitor)       # for cleaning variable names
library(geofacet)      # for special faceting with US map layout
library(dplyr)
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(ggplot2)
Sys.setlocale("LC_TIME", "English")
theme_set(theme_minimal())       
```

### Chart type
map

### Type of data
NA

### Reason for including the chart
TidyTuesday

### Link to data or source
[github repository page](https://github.com/rfordatascience/tidytuesday/tree/master/data/2022/2022-08-09)

### Research Question
What is the distribution of wheels around the world?

## Read in data for this week: 
```{r}
# Get the Data

# Read in with tidytuesdayR package 
#Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

tuesdata <- tidytuesdayR::tt_load('2022-08-09')
tuesdata <- tidytuesdayR::tt_load(2022, week = 38)

wasteWater <- tuesdata$HydroWASTE_v10
```
## Graph
```{r, fig.alt=""}
newWasteWater<-wasteWater %>% 
  group_by(COUNTRY) %>% 
  mutate(perCapita=WASTE_DIS/POP_SERVED)
newWasteWater %>% 
  ggplot(aes(x=LON_WWTP,y=LAT_WWTP,color=perCapita,size=RIVER_DIS))+
  geom_point()

newWasteWater %>% 
  ggplot(aes(x=perCapita,y=RIVER_DIS,label=CNTRY_ISO))+
  geom_point()+
  geom_text(check_overlap = TRUE)
  #geom_text(check_overlap = TRUE)

newWasteWate2<-newWasteWater %>% 
  filter(CNTRY_ISO=="BRA")

newWasteWate2 %>% 
  ggplot()+
  geom_point(aes(x=LON_WWTP,y=LAT_WWTP,color="red"))+
  geom_point(aes(x=LON_OUT,y=LAT_OUT))
```
## Research Question:
What is river discharge vs treated wastewater discharged per capita with in each country?

## Description:
Brazil and Belgium are two outliers in two opposite directions. Which is interesting since in Belgium there is nearly no recorded river outfall but the wastewater discharged is larger. Vice versa in Brazil.
